The Increased Effect of Elections and Changing Prime Ministers on Topics Discussed in the Australian Federal Parliament between 1901 and 2018

### 2019-10-31 outputs/docs/paper/paper_MA_structure_edit.Rmd
topics model

The goal of our modelling strategy is twofold. Firstly, we want to use topic modelling [@Blei2003latent] to summarise the Hansard text into meaningful topics that reduce the dimensionality of the text data and capture the main themes discussed in parliament over time. Secondly, we want to relate the resulting topic distributions to temporal trends, changes, and events, such as a change in prime minister, elections, and other external events.  The output of the first stage is the input to the second stage.

We first use a Correlated Topic Model (CTM) [@BleiLafferty2007] to obtain estimated topic distributions over time, and then further group these topics to match those of the Comparative Agendas Project. We consider these topic distributions as inputs that can be analysed by another model. Thus, the second modelling step involves using a Bayesian hierarchical Dirichlet model to analyse changes in the topic distributions (obtained from the first step) in relation to events of interest.

@@

## Overview of topic modelling
Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics. This means that each day's Hansard record needs to be classified by its topics. Sometimes Hansard records includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.

@@

In order to effectively categorise the topics of the entire Hansard, we use topic modelling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts. In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent. One advantage of using the Dirichlet distribution is that it formalises the idea that there is a trade-off in what is talked about in parliament given the limited time. A multinomial approach would not necessarily have this property.

@@

An overview, and an example, of how topic modelling works is available in Appendix \@ref(LDAoverviewandexample). The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and then Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics given documents. Finally, Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen.

One notable limitation of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic. However, in reality topics are often related.  For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking.

As such, we use the Correlated Topic Model (CTM) of @BleiLafferty2007 to obtain topic distributions. The CTM is a modification of LDA that allows for correlations between topics. More detail about the CTM is in Appendix \@ref(correlatedtopicmodelsection). There are various methods to help determine the appropriate number of topics to specify, and we further discuss the implications given our setting later in the paper. However the main implication is that the optimal number of topics was too large to be tractable by our analysis model, and too large to be easily visualised or examined. For this reason we manually group the topics identified by the CTM into those of the Comparative Agendas Project. It is these proportions that we use as an input to our analysis model.

>>>>

The goal of our modelling strategy is twofold. Firstly, we want to use topic modelling [@Blei2003latent] to summarise the Hansard text into meaningful topics that reduce the dimensionality of the text data and capture the main themes discussed in parliament over time. Secondly, we want to relate the resulting topic distributions to elections and changing prime ministers over time, accounting for temporal trends.

We first use a Correlated Topic Model [@BleiLafferty2007] to obtain estimated topic distributions over time, and then further group these topics to match those of the Comparative Agendas Project. We consider these topic distributions as inputs that can be analysed by another model. Thus, the second modelling step involves using a Bayesian hierarchical Dirichlet model to analyse changes in the topic distributions (obtained from the first step) in relation to events of interest.

@@

## Overview of topic modelling and topic selection
Although more- or less-fine levels of analysis are possible, here we are primarily interested in considering a day's topics. This means that each day's Hansard record needs to be classified by its topics. Sometimes Hansard records includes titles that make the topic clear. But not every statement has a title and the titles do not always define topics in a well-defined and consistent way, especially over longer time periods.

@@

In order to effectively categorise the topics of the entire Hansard, we use topic modelling, a statistical technique which aims to extract the underlying or latent 'topics' from a collection of texts. In particular, we use a method which is similar to Latent Dirichlet Allocation (LDA), first developed by @Blei2003latent.

<!-- One advantage of using the Dirichlet distribution is that it formalises the idea that there is a trade-off in what is talked about in parliament given the limited time. A multinomial approach would not necessarily have this property. -->

@@

An overview, and an example, of how topic modelling works is available in Appendix \@ref(LDAoverviewandexample). The underlying document generation process is discussed in Appendix \@ref(LDAdocgenprocess), and then Appendix \@ref(LDAposteriorestimation) explains how this is reversed to generate topics given documents.

One notable limitation of LDA is that the model assumes that the presence of one topic is not correlated with the presence of another topic. However, in reality topics are often related.  For instance, in the Hansard context, we may expect topics related to the army to be more commonly found with topics related to the navy, but less commonly with topics related to banking. As such, we use the Correlated Topic Model (CTM) of @BleiLafferty2007 to obtain topic distributions. The CTM is a modification of LDA that allows for correlations between topics. More detail about the CTM is in Appendix \@ref(correlatedtopicmodelsection).

### Categorisation of topics using the Comparative Agendas Project

There are various methods to help determine the appropriate number of topics to specify. Appendix \@ref(selecttopicnumber) contains a discussion of how the number of topics was chosen based on the output of the CTM. However, we found that the optimal number of topics selected was too large to be tractable by our analysis model, and too large to be easily visualised or examined. In addition, many of the topics in the optimal set referred to similar themes, such as budgeting or administrative topics.

For this reason we manually group the topics identified by the CTM into those of the Comparative Agendas Project. XX NEED TO EXPLAIN WHAT THIS IS - I HAVE NO IDEA XX
